### 2025-06-05 mycv/cv_latex.tex
Addition of Abrar's manuscript
paper status updates
updates

        \item
          \begin{twocolentry}{in preparation}
            \href{}{Deformation mechanism and texture evolution in AZ31 Mg alloy under uniaxial compression: experiments and simulations}
          \end{twocolentry}
          \begin{onecolentry}
            Jongbin Go*,  {\underline{\textit{Y. Jeong}*}}, Myeong-heom Park*, Sangwon Lee, Si Gao, Nobuhiro Tsuji
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{in preparation}
            \href{}{Reverse engineering material behavior using Bayesian inference and finite element analysis on ring-pull test}
          \end{twocolentry}
          \begin{onecolentry}
            B. Jeon, C. N. Tome, P. M. Beck, B. Eftinik, A. Talapatra, {\underline{\textit{Y. Jeong}*}}, L. Capolungo*
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{submitted}
            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}

>>>>

        \item
          \begin{twocolentry}{submitted}
            \href{}{Leveraging Machine Learning and Crystal Plasticity for Efficient Calibration of Yld2004-18p Anisotorpic Yield Function}
          \end{twocolentry}
          \begin{onecolentry}
            A. S. Ebrahim,  J. Kim, {\underline{\textit{Y. Jeong}}}, T. Park, H. Lim, B. L. Kinsey, J. Ha*
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{submitted}
            \href{}{Deformation mechanism and texture evolution in AZ31 Mg alloy under uniaxial compression: experiments and simulations}
          \end{twocolentry}
          \begin{onecolentry}
            Jongbin Go*,  {\underline{\textit{Y. Jeong}*}}, Myeong-heom Park*, Sangwon Lee, Si Gao, Nobuhiro Tsuji
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{submitted}
            \href{}{Reverse engineering material behavior using Bayesian inference and finite element analysis on ring-pull test}
          \end{twocolentry}
          \begin{onecolentry}
            B. Jeon, C. N. Tome, P. M. Beck, B. Eftinik, A. Talapatra, {\underline{\textit{Y. Jeong}*}}, L. Capolungo*
          \end{onecolentry}
          \vspace{0.10 cm}

        \item
          \begin{twocolentry}{Accepted}
            \href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        \begin{onecolentry}
            {\it International Journal of Plasticity}, in press
        \end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}
